---
title: "Linear regression via linear algebra"
date: "Last updated on `r Sys.Date()`"
output:
  html_document: 
    # code_folding: show
    df_print: kable
    highlight: tango
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: yes
---

```{r setup, include=FALSE}
# Set default behavior for all code chunks here:
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE, 
  fig.width = 16/2, 
  fig.height = 9/2
)

# Load all your used packages here:
library(tidyverse)
library(broom)
library(modelr)
```





***



# Preprocessing data

First, prepare the `training` data. Note that `data/train.csv` is the same as in PS7 on LASSO where it only had 50 rows. This is to speed up all computations.

```{r}
training <- read_csv("data/train.csv") %>% 
  # Define new outcome variable:
  mutate(logSalePrice = log(SalePrice+1)) %>% 
  # Select only needed variables
  select(logSalePrice, OverallQual, YearBuilt, GrLivArea)
```

Let's do a quick EDA of the variable `OverallQual`:

```{r}
ggplot(training, aes(x = OverallQual)) +
  geom_bar() +
  labs(x = "Overall quality", title = "Distribution of overall quality")
```

Let's convert `OverallQual` to a binary categorical variable:

```{r}
training <- training %>% 
  mutate(OverallQual = if_else(OverallQual < 5, "bad", "good"))

ggplot(training, aes(x = OverallQual)) +
  geom_bar() +
  labs(x = "Overall quality", title = "Distribution of overall quality")
```



## Linear regression results

Define model formula:

```{r}
model_formula <- "logSalePrice ~ OverallQual + YearBuilt + GrLivArea" %>% 
  as.formula()
```

Output regression table:

```{r}
model_lm <- lm(model_formula, data = training)
tidy(model_lm, conf.int = TRUE)
```

Your goal is to compute the values in the `estimate` column using the matrix algebra from Lec 28 `regression_linear_algebra.Rmd`. In other words, output a 4 x 1 vector of the values in the second column of the above regression table. Note: in order to perform matrix multiplications, you need to convert all "tibble" data frames to matrix objects using `as.matrix()` first.

```{r}

```




